%%%%%%%%%%%%%%%%%%%% Stroke Funding %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Stroke funding}

\begin{itemize}
    \item NIHR Health Services and Delivery Research Reference NIHR153982 £539k: Modelling the resource requirements for implementation of mobile stroke units across the National Health Service, their cost-effectiveness, and their effect on equity of access to emergency stroke care. April 2023 to September 2024. \url{https://fundingawards.nihr.ac.uk/award/NIHR153982}

    \item NIHR Health Services and Delivery Research Reference NIHR134326: £589K Stroke Audit Machine Learning (SAMueL-2). April 2022 to March 2024. \url{https://fundingawards.nihr.ac.uk/award/NIHR134326}.

    \item NIHR Programme Grants for Applied Research NIHR202361: £1.983M OPTimising IMplementation of Ischaemic Stroke Thrombectomy (OptImIST). April 2021 to March 2026. \url{https://fundingawards.nihr.ac.uk/award/NIHR202361}

    \item NIHR Programme Development Grant NIHR201692: £132K Enhancing and disseminating the outputs of the Promoting Effective and Rapid Stroke Care (PEARS) NIHR PGfAR Programme Grant \& facilitating thrombectomy implementation in England. Dec 2020 to Nov 2021. \url{https://fundingawards.nihr.ac.uk/award/NIHR201692}

    \item NIHR HS\&DR Project: 17/99/89: £330K Use of simulation and machine learning to identify key levers for maximising the disability benefit of intravenous thrombolysis in acute stroke pathways. Feb 2019 - August 2021 \url{https://fundingawards.nihr.ac.uk/award/17/99/89}

    \item We have received £200-£250K funding for commissioned work by NHS England, NHS Scotland, NHS Wales, Health and Social Care in Northern Ireland, NHS England East of England Region, NHS England London Region, South West Cardiac Strategic Clinical Network.
    
\end{itemize}

