%%%%%%%%%%%%%%%%%%%%% Non stroke publications and finding %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Non-stroke publications and funding}

\subsection{Peer-reviewed publications}

\begin{itemize}
    \item Monks, T., Harper, A., Allen, M., Collins, L, Mayne, A. Forecasting the daily demand for emergency medical ambulances in England and Wales: a benchmark model and external validation. BMC Med Inform Decis Mak 23, 117 (2023). \url{https://doi.org/10.1186/s12911-023-02218-z}

    \item Zhelev, Z., Peters, J., Rogers, M, Allen, M., Kijauskaite, G., Seedat F., Wilkinson, E. , Hyde, C. (2023) Test accuracy of artificial intelligence-based grading of fundus images in diabetic retinopathy screening: A systematic review. Journal of Medical Screening. \url{https://journals.sagepub.com/doi/10.1177/09691413221144382}.  DOI: 10.1177/09691413221144382/ ID: JMS-22-123.R3. 

    \item Allen M, Bhanji A, Willemsen J, Dudfield S, Logan S \& Monks T (2020) A simulation modelling toolkit for organising outpatient dialysis services during the COVID-19 pandemic. PLOS ONE 15(8): e0237628. \url{https://doi.org/10.1371/journal.pone.0237628}

    \item Allen M, Villeneuve E, Pitt M, \& Thornton, S. (2020) How can consultant-led childbirth care at time of delivery be maximised? A modelling study. BMJ Open 2020;10:e034830. doi: 10.1136/bmjopen-2019-034830 \url{https://bmjopen.bmj.com/content/10/7/e034830}

    \item Mujica-Mota, R., Lando, P., Pitt, M., Allen, M. \& Spencer, A. (2020) The heterogeneous effects of neonatal care: a model of endogenous demand for multiple treatment options based on geographical access to care. Health Economics 29:46-60 \url{https://doi.org/10.1002/hec.3970}

    \item Villeneuve, E., Landa, P., Allen, M., Specncer, A., Prosser, S., Gibson, A., Kesley, K., Mujica-Mota, R., Manktelow, B., Modi, N., Thornton, S. \& Pitt, M. (2018) A framework to address key issues of neonatal service configuration in England: the NeoNet multimethods study. Health Serv Deliv Res 6: doi:10.3310/hsdr06350 \url{https://www.journalslibrary.nihr.ac.uk/hsdr/hsdr06350}

    \item Swancutt, D., Joel-Edgar, S., Allen, M., Thomas, D., Brant, H. Benger, J., Byng, R. \& Pinkney, J. (2017) Not all waits are equal: an exploratory investigation of emergency care patient pathways. BMC Health Services Research 17:436 doi:10.1186/s12913-017-2349-2 \url{https://bmchealthservres.biomedcentral.com/articles/10.1186/s12913-017-2349-2}

    \item Jonathan Pinkney, Susanna Rance, Jonathan Benger, Heather Brant, Sian Joel-Edgar, Dawn Swancutt, Debra Westlake, Mark Pearson, Daniel Thomas, Ingrid Holme, Ruth Endacott, Rob Anderson, Michael Allen, Sarah Purdy, John Campbell, Rod Sheaff, Richard Byng (2016)  How can frontline expertise and new models of care best contribute to safely reducing avoidable acute admissions? A mixed-methods study of four acute hospitals. Health Services and Delivery Research, volume 4, number 3. \url{https://pubmed.ncbi.nlm.nih.gov/26844315/}

    \item Allen M, Spencer A, Gibson A, Matthews J, Allwood A, Prosser S, Pitt, M. (2015) Right cot, right place, right time: improving the design and organisation of neonatal care networks – a computer simulation study. Health Serv Deliv Res 2015;3(20) \url{https://www.ncbi.nlm.nih.gov/books/NBK293953/}

\end{itemize}

\subsection{Non-peer-reviewed publications (medRxiv, etc.)}

\begin{itemize}
    \item Allen M, Pearn K, Monks T. (2021) Developing an OpenAI Gym-compatible framework and simulation environment for testing Deep Reinforcement Learning agents solving the Ambulance Location Problem. arXiv:210104434 \url{http://arxiv.org/abs/2101.04434}
    
    \item Allen, M. \& Salmon, A. (2020) Synthesising artificial patient-level data for Open Science - an evaluation of five methods. medRxiv doi: \url{https://doi.org/10.1101/2020.10.09.20210138}

    \item Allen M, Monks T. (2020) Integrating Deep Reinforcement Learning Networks with Health System Simulations. arXiv:200807434 [cs] Published Online First: 21 July 2020. \url{http://arxiv.org/abs/2008.07434}
    
\end{itemize}


\subsection{Funding}

\begin{itemize}
    \item NIHR HS\&DR 14/19/08: £336,577. NeoNet: The right cot, at the right time, at the right place 2. Providing a national demand/capacity model for neonatal care in England. Pitt MA, Allen M, Spencer A, Gibson A, Prosser S, Manktelow B, Thornton S, Modi N. (2014-2017) \url{https://fundingawards.nihr.ac.uk/award/14/19/08}

    \item NIHR SDO 10/1011/48: £133,468. The right cot, at the right time, at the right place. Use of Neonatal Survey data and computer simulation technology to improve design and organisation of neonatal care networks. Pitt MA, Gibson A, Allen M, Manktelow BN, Allwood ACL, Spencer A, Prosser S. (2011-2014) \url{https://fundingawards.nihr.ac.uk/award/10/1011/48}
\end{itemize}

